---
title: "Titanic"
author: "Haomin Zhang"
format: html
editor: visual
---

## Machine Learning from Disaster

Use machine learning to create a model that predicts which passengers survived the Titanic shipwreck.

## Background

The sinking of the Titanic is one of the most infamous shipwrecks in history.

On April 15, 1912, during her maiden voyage, the widely considered “unsinkable” RMS Titanic sank after colliding with an iceberg.

Unfortunately, there weren’t enough lifeboats for everyone onboard, resulting in the death of 1502 out of 2224 passengers and crew.

While there was some element of luck involved in surviving, it seems some groups of people were more likely to survive than others.

## Challenge

Build a predictive model that answers the question: “what sorts of people were more likely to survive?”
using passenger data.

## Code

```{r}
#| echo: false
#| output: false
library(tidyverse)
library(tidymodels)
library(conflicted)
conflicts_prefer(dplyr::filter())
conflicts_prefer(dplyr::lag())
conflicts_prefer(recipes::step())
```

### Read Data

```{r}
titanic_train <- read.csv("./titanic_train.csv")
glimpse(titanic_train)
```

### Convert Data

```{r}
titanic_train[titanic_train==""] <- NA
titanic_train <- titanic_train |>
  mutate(
    Survived=case_match(
      Survived,
      0 ~ "No",
      1 ~ "Yes"
    ),
    Survived=as.factor(Survived),
    Survived=fct_rev(Survived),
    Pclass=as.factor(Pclass),
    Sex=as.factor(Sex),
    Sex=fct_rev(Sex),
    Age=case_when(
      Age/10 <= 1 ~ "0-10",
      Age/10 <= 2 ~ "10-20",
      Age/10 <= 3 ~ "20-30",
      Age/10 <= 4 ~ "30-40",
      Age/10 <= 5 ~ "40-50",
      Age/10 <= 6 ~ "50-60",
      Age/10 > 6 ~ "60+",
      is.na(Age) ~ NA,
    ),
    Age=as.factor(Age),
    Family=SibSp + Parch,
    Family=case_when(
      Family == 0 ~ "Single",
      Family <= 3 ~ "Small",
      between(Family, 4, 6) ~ "Medium",
      Family >= 7 ~ "Large"
    ),
    Family=as.factor(Family),
    Family=fct_rev(Family) |> fct_relevel("Single"),
    Embarked=case_match(
      Embarked,
      "C" ~ "Cherbourg",
      "Q" ~ "Queenstown",
      "S" ~ "Southampton",
      .default=NA,
    ),
    Embarked=as.factor(Embarked)
  )
glimpse(titanic_train)
```

### Draw Plot

```{r}
titanic_train |>
  ggplot(aes(x=Age, fill=Sex)) +
  geom_bar(position = "dodge") +
  theme_bw()
titanic_train |>
  ggplot(aes(x=Age, group=Survived, fill=Survived)) +
  geom_bar(aes(y=after_stat(prop)), position="dodge") +
  theme_bw()
titanic_train |>
  ggplot(aes(x=Sex, group=Survived, fill=Survived)) +
  geom_bar(aes(y=after_stat(prop)), position="dodge") +
  theme_bw()
titanic_train |>
  ggplot(aes(x=Family, group=Survived, fill=Survived)) +
  geom_bar(aes(y=after_stat(prop)), position="dodge") +
  theme_bw()
titanic_train |>
  ggplot(aes(x=Pclass, group=Survived, fill=Survived)) +
  geom_bar(aes(y=after_stat(prop)), position="dodge") +
  theme_bw()
titanic_train |>
  ggplot(aes(x=Embarked, group=Survived, fill=Survived)) +
  geom_bar(aes(y=after_stat(prop)), position="dodge") +
  theme_bw()
```

### Split Data

```{r}
data <- titanic_train |>
  select(Survived, Age, Sex, Family, Pclass, Embarked)
set.seed(1024)
split <- initial_split(data)
folds <- vfold_cv(data, strata=Survived)
```

### Create Recipe & Workflow

```{r}
recipe <- recipe(Survived ~ ., data=split) |>
  step_impute_knn(
    Age, Embarked, 
    impute_with=imp_vars(Sex, Family, Pclass)
  )
dummy <- recipe |>
  step_dummy(
    all_nominal_predictors(),
    one_hot=TRUE
  )
work <- \(model, recipe) {
  workflow <- workflow() |>
    add_recipe(recipe) |>
    add_model(model)
  workflow |>
    last_fit(split) |>
    collect_metrics() |>
    print()
  workflow |>
    fit_resamples(folds) |>
    collect_metrics() |>
    print()
}
```

### Create Model

```{r}
# Random Forest
rand_forest(
  mode="classification", engine="ranger"
) |> work(recipe)
# Boosted Trees
boost_tree(
  mode="classification", engine="xgboost"
) |> work(dummy)
```
